### 2014-12-01 writing/F'14 paper/sick.tex
Paper update, bug fixes.

\begin{table*}[htp]
  \centering
  \begin{tabular}{l}
    \toprule
example example example example example example example example example example example \\
example example example example example example example example example example example \\
ENTAILMENT A skilled person is riding a bicycle on one wheel	A person is riding the bicycle on one wheel\\
CONTRADICTION The player is missing the basket and a crowd is in background	The player is dunking the basketball into the net and a crowd is in background\\
    \bottomrule
  \end{tabular}
  \caption{\label{examplesofsickdata}Examples of successful classifications on SICK.}
\end{table*}

@@

\begin{table}[tp]
  \centering \small
  \begin{tabular}{ l r@{ \ } r@{ \ } r@{ \ } }
    \toprule
    ~&\multicolumn{1}{c}{$\natind$ only} & \multicolumn{1}{c}{??d RNN}  & \multicolumn{1}{c}{??d RNTN}\\
    \midrule
    Test & 56.7 &	...& \textbf{...} \\
    Train &- &- &-  \\
    \bottomrule
  \end{tabular}
  \caption{Performance on SICK.}
  \label{sresultstable}
\end{table}

@@

Explain Table \ref{examplesofsickdata}. 
Explain Table \ref{examplesofsickdata}. 
Explain Table \ref{examplesofsickdata}. 
Explain Table \ref{examplesofsickdata}. 
Explain Table \ref{examplesofsickdata}. 
Explain Table \ref{examplesofsickdata}. 
Explain Table \ref{examplesofsickdata}. 
Explain Table \ref{examplesofsickdata}. 
Explain Table \ref{examplesofsickdata}. 
Explain Table \ref{examplesofsickdata}. 
Explain Table \ref{examplesofsickdata}. 
Explain Table \ref{examplesofsickdata}. 
Explain Table \ref{examplesofsickdata}. 
Explain Table \ref{examplesofsickdata}. 
Explain Table \ref{examplesofsickdata}.

>>>>

\begin{table*}[htp]
  \centering\small
  \begin{tabular}{lcl}
    \toprule
A woman is not boiling shrimps.& \ii{contradiction}&	A woman is boiling shrimps.\\
A wild deer is jumping a fence. &\ii{entailment}	&A deer is jumping a fence.\\
A potato is being sliced by a woman. &\ii{entailment}	&A woman is slicing a potato.\\
The plane, which is south African, is flying in a blue sky.& \ii{entailment}&	An airplane is flying through the air.\\
    \bottomrule
  \end{tabular}
  \caption{\label{examplesofsickdata}Examples of successful classifications on SICK.}
\end{table*}

@@

\begin{table}[tp]
  \centering \small
  \begin{tabular}{ l r@{ \ } r@{ \ } r@{ \ } }
    \toprule
    ~&\multicolumn{1}{c}{$\natind$ only} & \multicolumn{1}{c}{??d RNN}  & \multicolumn{1}{c}{??d RNTN}\\
    \midrule
    Test & 56.7 &	...& \textbf{75.5} \\
    Train &- &- &-  \\
    \bottomrule
  \end{tabular}
  \caption{Performance on SICK.}
  \label{sresultstable}
\end{table}

@@

Table \ref{examplesofsickdata} shows a few typical examples of correct classifications. The model appears to be able to successfully recognize negation and the insertion and deletion of words, as demonstrated in the first two examples. The latter two show that the model still recognize entailments and contradictions between sentences which are not superficially similar, such as passive--active pairs and sentences with low lexical overlap.
